Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/paper.tex
Update acks

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast evaluation. The research was
  supported by Centers for Disease Control and Prevention (CDC) grant
  U01IP001121, and gifts from Facebook and Google.}

>>>>

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast evaluation. The research was
  supported by Centers for Disease Control and Prevention (CDC) grant
  U01IP001121, gifts from Facebook, Google, McCune, and Optum, and National
  Science Foundation Graduate Research Fellowship Program (NSF GRFP) award
  DGE175016.}
